---
title: "Meeting 09-08-23"
output:
  pdf_document: default
  html_document: default
date: "2023-08-07"
---

```{r setup, include=FALSE}
# Load in packages and data
library(cmdstanr)
library(posterior)
library(bayesplot)
library(ggplot2)
library(data.table)
```

## 1.1 Is there still as sizeable proportion of infections occuring within household?

After 2015ish, from R16

Using the logit model which includes all the data. Recall from the previous Rmd:

1 : Female to male, out-of-household
2 : Female to male, same household 
3 : Male to female, out-of-household
4 : Male to female, same household

```{r}
# Load CmdStanR fits
fit_norm <- readRDS(here::here("data", "logit_pairs_draws_ordered.rds"))
#fit_beta <- readRDS(here::here("data", "beta_pairs_draws_ordered.rds"))

# Extract rates (eta)
eta_draws <- as_draws_matrix(fit_norm$draws("eta"))
eta_sums <- rowSums(eta_draws)

eta_prop <- eta_draws / eta_sums

# Check proportion of HH vs OOH
eta_HH_prop <- rowSums(eta_prop[, c(2,4)])
summary(eta_HH_prop)
print(quantile(eta_HH_prop, c(0.025, 0.975))) # 95% CI
```

Is there a specific time which we should start the modelling from (i.e a date/round for which we start counting the intervention as 'significant'?)

## 1.2 Does HH proportion change with community (fishing vs inland?)

First we observe a quirk with the data:

```{r}
# Load in pairs data
filename <- here::here("data", "pairs_tsi.csv")
pairs_tsi <- read.csv(filename)
setDT(pairs_tsi)

# Check whether same household pairs are the same community
same_hh_pairs <- pairs_tsi[same_hh == 1]
source_comm <- same_hh_pairs[,.(COMM.SOURCE)]
recip_comm <- same_hh_pairs[,.(COMM.RECIPIENT)]

t(source_comm == recip_comm) # Observation 81 is false
```

The 81st entry of the same_hh data set has a source and recipient from the same household but different community! Do we ignore this data point? (Yes in this 
model).

We should fit the model to four groups:

- Same household, fishing (1)
- Same household, inland (2)
- Different household, fishing* (4)
- Different household, inland* (5)

But how do we decide which community if the source and recipient are not from
the same community? Just from source/recipient community or add a seperate group
from an inter-community transmission (3). (The model picked uses the last option, so
we now have five groups)


```{r}
# Load CmdStanR fit
fit_1_2 <- readRDS(here::here("data", "logit_pairs_draws_1-2.rds"))
print(fit_1_2, max_rows = 1000)
```

Now we calculate confidence intervals for the proportion of HH infections for
both fishing and inland communities:

```{r}
# Extract rates (eta)
eta_draws <- as_draws_matrix(fit_1_2$draws("eta"))
eta_sums <- rowSums(eta_draws)

eta_prop <- eta_draws / eta_sums

# Check proportion of HH vs OOH for both fishing and inland
eta_HH_fishing <- eta_prop[, 1] / rowSums(eta_prop[, c(1, 4)])
eta_HH_inland <- eta_prop[, 2] / rowSums(eta_prop[, c(2, 5)])

print(quantile(eta_HH_fishing, c(0.025, 0.975))) # 95% CI
print(quantile(eta_HH_inland, c(0.025, 0.975))) # 95% CI
```

The confidence intervals have a good amount of overlap which suggests there 
might not be any change in proportion of infections which are within HH between
the two communities.

## 1.3 Is the proportion of HH transmissions larger MF or FM?

We use the same model and draws from Q1.1:

```{r}
# Extract rates (eta)
eta_draws <- as_draws_matrix(fit_norm$draws("eta"))
eta_sums <- rowSums(eta_draws)

eta_prop <- eta_draws / eta_sums

# Check proportion of HH vs OOH for both MF and FM
eta_HH_MF <- eta_prop[, 4] / rowSums(eta_prop[, c(3, 4)])
eta_HH_FM <- eta_prop[, 2] / rowSums(eta_prop[, c(1, 2)])

print(quantile(eta_HH_MF, c(0.025, 0.975))) # 95% CI
print(quantile(eta_HH_FM, c(0.025, 0.975))) # 95% CI
```

Again, there is a significant overlap it seems so potentially not a huge
difference.

## 3

We use the same fit as above. We treat "young" as being aged 15-24.

```{r}
#library(parallel)
#n_cores <- detectCores() - 1
source(here::here("helper-functions", "plot_normal.R"))

ages <- seq(15.5, 49.5, by = 1)
draws <- seq(100, 5000, by = 100)
grid <- expand.grid(ages, ages)

final_intensities <- list() # one entry per group
eta_draws <- as_draws_matrix(fit_norm$draws("eta"))

for (group in 1:4){
  # Calculate densities for 50 iterations
  intensities <- lapply(draws, plot_normal, fit = fit_norm, chain_no = 1, 
                  group_no = group, ages = ages, plot = FALSE)
  etas <- as.numeric(eta_draws[draws, group])
  
  for (index in 1:length(etas)){
    intensities[[index]] <- etas[index] * intensities[[index]]
  }
  
  # Calculate mean density
  intensity_matrix <- matrix(unlist(intensities), nrow = 50, byrow = TRUE)
  final_intensity <- apply(intensity_matrix, 2, mean)
  final_intensities[[group]] <- final_intensity
}
```

# 3.1 Are young men predominantly affected by older women through non-HH?

We want the F -> M groups for HH and non-HH respectively (so group 1 for OOH and
group 2 for HH)

```{r}
# Extract relevant intensities and combine into one data.table
intensity_FM_OOH <- final_intensities[[1]]
intensity_FM_HH <- final_intensities[[2]]

recip_15_24_indices <- which(grid$Var2 < 24) # X: Source, Y: Recipient

yng_grid <- grid[recip_15_24_indices, ]
yng_grid$FM_OOH <- intensity_FM_OOH[recip_15_24_indices]
yng_grid$FM_HH <- intensity_FM_HH[recip_15_24_indices]

setDT(yng_grid)

# Calculate intensities among young people by age of source
yng_grid[, FM_OOH_sum := sum(FM_OOH), by = Var1]
yng_grid[, FM_HH_sum := sum(FM_HH), by = Var1]

# Drop unnecessary columns
#yng_grid[, c("FM_OOH", "FM_HH", "Var2") := NULL]

# Plot intensities

p <- ggplot(yng_grid, aes(x = Var1)) + 
  geom_line(aes(y = FM_OOH_sum, color = "Out-of-household")) +
  geom_line(aes(y = FM_HH_sum, color = "Within household")) +
  labs(x = "Age of source (Female)", y = "Relative intensity",
       title = "FM transmission HH vs non-HH intensity",
       caption = "Among young (16-24) recipients",
       color = NULL)
p
```

Now repeat the analysis for M -> F transmissions

```{r}
# Extract relevant intensities and add to previous data.table
intensity_MF_OOH <- final_intensities[[3]]
intensity_MF_HH <- final_intensities[[4]]

yng_grid$MF_OOH <- intensity_MF_OOH[recip_15_24_indices]
yng_grid$MF_HH <- intensity_MF_HH[recip_15_24_indices]

# Calculate intensities among young people by age of source
yng_grid[, MF_OOH_sum := sum(MF_OOH), by = Var1]
yng_grid[, MF_HH_sum := sum(MF_HH), by = Var1]

# Drop unnecessary columns
#yng_grid[, c("MF_OOH", "MF_HH", "Var2") := NULL]

# Plot intensities

p <- ggplot(yng_grid, aes(x = Var1)) + 
  geom_line(aes(y = MF_OOH_sum, color = "Out-of-household")) +
  geom_line(aes(y = MF_HH_sum, color = "Within household")) +
  labs(x = "Age of source (Male)", y = "Relative intensity",
       title = "MF transmission HH vs non-HH intensity",
       caption = "Among young (16-24) recipients",
       color = NULL)
p
```