---
title: "Meeting 09-08-23"
output: html_document
date: "2023-08-07"
---

```{r setup, include=FALSE}
# Load in packages and data
#library(cmdstanr)
library(posterior)
library(bayesplot)
library(ggplot2)
library(data.table)
```

## 1.1 Is there still as sizeable proportion of infections occuring within household?

Using the logit model which includes all the data:

```{r}
# Load CmdStanR fits
fit_norm <- readRDS(here::here("data", "logit_pairs_draws_ordered.rds"))
#fit_beta <- readRDS(here::here("data", "beta_pairs_draws_ordered.rds"))

# Extract rates (eta)
eta_draws <- as_draws_matrix(fit_norm$draws("eta"))
eta_sums <- rowSums(eta_draws)

eta_prop <- eta_draws / eta_sums

# Check proportion of HH vs OOH
eta_HH_prop <- rowSums(eta_prop[, c(2,4)])
summary(eta_HH_prop)
print(quantile(eta_HH_prop, c(0.025, 0.975))) # 95% CI
```

Is there a specific time which we should start the modelling from (i.e a date/round for which we start counting the intervention as 'significant'?)

## 1.2 Does HH proportion change with community (fishing vs inland?)

First we observe a quirk with the data:

```{r}
# Load in pairs data
filename <- here::here("data", "pairs_tsi.csv")
pairs_tsi <- read.csv(filename)
setDT(pairs_tsi)

# Check whether same household pairs are the same community
same_hh_pairs <- pairs_tsi[same_hh == 1]
source_comm <- same_hh_pairs[,.(COMM.SOURCE)]
recip_comm <- same_hh_pairs[,.(COMM.RECIPIENT)]

source_comm == recip_comm
```

The 81st entry of the same_hh data set has a source and recipient from the same household but different community! Do we ignore this data point? (Yes in this 
model).

We should fit the model to four groups:

- Same household, fishing
- Same household, inland
- Different household, fishing*
- Different household, inland*

But how do we decide which community if the source and recipient are not from
the same community? Just from source/recipient community or add a seperate group
from an inter-community transmission. (The model picked uses the last option, so
we now have five groups)


```{r}
# Load CmdStanR fit
fit_1-2 <- readRDS(here::here("data", "logit_pairs_draws_1-2.rds"))
```